---
title: "tractor_arima"
author: "Christopher Chan"
date: "February 14, 2019"
output:
    github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

http://ucanalytics.com/blogs/step-by-step-graphic-guide-to-forecasting-through-arima-modeling-in-r-manufacturing-case-study-example/
```{r, message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(tseries)
```

Read in data and get it into ts format.
```{r, results='hide'}
here()
data <- read_csv('Tractor-Sales.csv')

data_ts <- ts(data[,2], start=c(2003, 1), frequency=12)
plot(data_ts)
```

dff() data to get a constant mean, eventually make it stationary.
```{r}
plot(diff(data_ts))
```

log transforming to remove the variance.
```{r}
plot(log10(data_ts))
```

log transforming and diff() to make it stationary. The result is much better.
```{r}
st_data_ts <- diff(log10(data_ts))

plot(st_data_ts)
```

Validate stationarity with a ADF test. With a p-value < 0.05 we can reject the null and conclude the results are stationary.
```{r}
adf.test(st_data_ts, alternative='stationary')
```

Determine degrees of ARIMA from ACF and PACF plots
```{r}
par(mfrow=c(1,2))
acf(st_data_ts)
pacf(st_data_ts)
```



